What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-07 android-stacks.tex
Stack traces historgarms

@@

\subsection{Internal Validity} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases.

\subsection{External Validity} The results presented here were based on mining
issues on Github through the GHTorrent dataset. While comprehensive and
extensive, GHTorrent is not an exact replica of Github, so several issues might
be left out. Due to the way data collection works with GHTorrent, for projects
that are relatively inactive, GHTorrent might have not collected a significant
proportion of their issues. We did not investigate the extend of this threat on
our sample.

\subsection{Construct Validity}
Parts of our analysis are based on the availability of stack traces on issues on
Github. In using this dataset, we make an underlying assumption: the
stack traces reported on issues are representative of real crashes in
the applications. The assumption is impossible to mitigate without access to
the full set of crash data per application. Services exist to collect all
crash data from applications, so access to such a dataset will allow for
a thorough replication of our analysis, perhaps at the individual application
level.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5]{stack-size-wrappings-hist.pdf}
  \end{center}
  \caption{Stack sizes (top) and wrappings (bottom) for Java (left) and Android (right) stack traces}
  \label{fig:sizewrapbhists}
\end{figure}

@@

\noindent\emph{Internal Validity} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases.

\noindent\emph{External Validity} The results presented here were based on mining
issues on Github through the GHTorrent dataset. While comprehensive and
extensive, GHTorrent is not an exact replica of Github, so several issues might
be left out. Due to the way data collection works with GHTorrent, for projects
that are relatively inactive, GHTorrent might have not collected a significant
proportion of their issues. We did not investigate the extend of this threat on
our sample.

\noindent\emph{Construct Validity} Parts of our analysis are based on the availability of stack traces on issues on
Github. In using this dataset, we make an underlying assumption: the
stack traces reported on issues are representative of real crashes in
the applications. The assumption is impossible to mitigate without access to
the full set of crash data per application. Services exist to collect all
crash data from applications, so access to such a dataset will allow for
a thorough replication of our analysis, perhaps at the individual application
level.
